How Significant was WW2 in the Development of the Computer?

### 2017-02-21 Draft 2/Section 3 - Universality.tex
I honestly don't know what I've changed but here's a commit becuase y not

\subsubsection{storing & accessing \textit{m}-configurations}
\subsubsubwithchickenandmayopleasethanks{eating & fulfilling life goals #subwaydatesboiiiiis love man chllz peace wavey donss}

>>>>

\subsubsection{Storing \& Accessing \textit{m}-configurations}
%\subsubsubwithchickenandmayopleasethanks{eating & fulfilling life goals #subwaydatesboiiiiis love man chllz peace wavey donss}
Once again, in order to store the information and operations associated with each \textit{m}-configuration, we shall use another list. The first element of the list shall represent $q_0$, the second $q_1$ and so on.
Each element of the list will be a pair: firstly, the symbol which should be checked for, as a real number; secondly, the transformation that should be performed on the tape. This transformation will be of the form $(\bm{C})(\{\bm{M}_L/\bm{M}_R/\bm{M}_S\})(\bm{W}a)$, which applies first a write transformation first, before a movement transformation and the tape length correction transformation.
